---
title: CV
name: Joshua
surname: Cook
position: "Graduate Student"
address: "Boston, MA"
phone: (818) 437-7904
www: www.joshuacook.netlify.app
email: "josh.hr.cook@gmail.com"
# twitter: JoshDoesA
github: jhrcook
# linkedin: joshua-hr-cook
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am a graduate student at Harvard Medical School using Bayesian statistical modeling to study cancer genetics."
docname: my-cv
output:
  vitae::markdowncv:
    theme: davewhipp
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(here)
library(tidyverse)
library(vitae)
```

## Summary

As an undergraduate at UC Irvine, I double-majored in biology and chemistry and researched the interactions between the human immune system and the parasite *Toxoplasma gondii*.
In graduate school, I have switched to studying cancer biology using computational methods.
While learning about statistics and mathematical modeling, I was naturally drawn to Bayesian statistical modeling which has since become a passion of mine.

## Education

```{r}
library(tibble)
tribble(
  ~ degree, ~ year, ~ institution, ~ location,
  "B.S. Biochemistry & Molecular Biology", "2013-2017", "University of California, Irvine", "Irvine, CA",
  "B.S. Chemistry", "2013-2017", "University of California, Irvine", "Irvine, CA",
  "Ph.D. Cancer Genetics & Bioinformatics", "2017-present", "Harvard Medical School", "Boston, MA",
) %>%
  detailed_entries(what=degree, when=year, with=institution, where=location)
```

## Publications

```{r publications}
bibliography_entries(here("publications.bib"))
```
